\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.18in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Amit Badoni} \\ \vspace{1pt}
    \small \href{mailto:amitbadoni1699@gmail.com}{amitbadoni1699@gmail.com} $|$ 
    \href{https://linkedin.com/kriti1799}{linkedin.com/kriti1799} $|$
    \href{https://github.com/kriti1799}{github.com/kriti1799} $|$
    +1 470-301-3942 $|$ Atlanta, USA
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, USA}
      {Master of Science in Analytics}{December 2026}
    \resumeSubheading
      {Indian Institute of Technology Kanpur}{Kanpur, India}
      {B.Tech. \& M.Tech. (Dual Degree) in Chemical Engineering}{July 2022}
      \small{\textbf{GPA:} M.Tech. 10/10, B.Tech. 8.5/10}
  \resumeSubHeadingListEnd

\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Smartworks Coworking Spaces}{Gurgaon, India}
      {Founder's Office Intern \textendash Strategic Initiatives \& Innovation}{April 2025 - June 2025}
      \resumeItemListStart
        \resumeItem{Directed a CRM AI agent pilot utilizing LLM-generated natural language to SQL conversion for real-time metric access.}
        \resumeItem{Initiated AI SaaS tools for design and HR processes, achieving 30\% \& 80\% respective reductions in turnaround time.}
        \resumeItem{Engineered an automated pipeline to convert raw attendance data into Power BI dashboards and REST API-triggered WhatsApp alerts, reducing manpower shortage resolution time by 25\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Rocket Learning}{Bangalore, India}
      {Data Product Manager}{March 2024 - April 2025}
      \resumeItemListStart
        \resumeItem{Constructed Power BI dashboards leveraging SQL on millions of user-event records to oversee 10+ features and resolved 50+ developer issues.}
        \resumeItem{Deployed a WhatsApp-based RAG AI agent for education workers, creating dashboards in Looker Studio via Google BigQuery SQL queries, with 3,000+ users onboarded and reaching 10\% DAU in 2 months.}
        \resumeItem{Collaborated with data engineers to architect ETL pipelines for AWS Redshift transition orchestrated by Airflow; automated 100+ metrics for A/B testing and reporting with SQL, resulting in a 15\% experiment uplift.}
      \resumeItemListEnd

    \resumeSubheading
      {McKinsey \& Company}{Mumbai, India}
      {Business Analyst - 2}{September 2022 - March 2024}
      \resumeItemListStart
        \resumeItem{Achieved 2\% reduction in coal consumption for an energy client by implementing a CART model to optimize process parameters.}
        \resumeItem{Contributed to a GenAI impact report for NASSCOM; aggregated insights from internal pilots and over 15 CxO interviews.}
        \resumeItem{Generated a \$1M EBITDA pipeline for an auto supplier; coordinated with 15+ stakeholders and delivered 40\% in value.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {Interpretable Machine Learning for U.S. Life Expectancy (County-Level Analysis)}{}
      \resumeItemListStart
        \resumeItem{Integrated multi-source public health datasets from various sources to create a robust modeling dataset. Applied supervised and unsupervised learning techniques achieving MAE \textasciitilde 1.3 years and R\textsuperscript{2} \textasciitilde 0.7 under k-fold cross validation. Deployed model outputs in an interactive dashboard showcasing predicted life expectancy and key contributing factors across U.S. counties.}
      \resumeItemListEnd

    \resumeProjectHeading
      {Semantic Segmentation using PSPNet with ResNet Backbone}{}
      \resumeItemListStart
        \resumeItem{Executed a PSPNet-based semantic segmentation model using a ResNet-50 backbone in PyTorch, integrating dilated convolutions and pyramid pooling. Achieved \textasciitilde56\% mean IoU on the CamVid dataset, improved to \textasciitilde63-65\% after fine-tuning.}
      \resumeItemListEnd

    \resumeProjectHeading
      {Automated Job Application Tracker}{}
      \resumeItemListStart
        \resumeItem{Engineered a workflow using LangChain with OAuth2 and Google Sheets API to streamline job application tracking, enhancing structured extraction, classification, and state updates.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Skills}
  \resumeSubHeadingListStart
    \resumeItemListStart
      \resumeItem{\textbf{Technical Skills:} Python, SQL, Machine Learning, Data Analysis}
      \resumeItem{\textbf{Tools:} Power BI, Looker Studio, Google BigQuery, AWS Redshift, Airflow, PyTorch}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}